---
title: "BIODIVERSITY TRENDS IN FAO GLOBAL CAPTURE FISHERIES PRODUCTION STATISTICAL DATA"
subtitle: "(Draft version)"
output: 
  pdf_document:
    fig_caption: yes
    highlight: kate
    number_sections: yes
    toc: yes
    toc_depth : 3
geometry: margin=1.75cm
fontsize: 11pt
header-includes:
    \usepackage{lipsum}
    \usepackage{placeins}
    \usepackage{floatrow}
    \usepackage{caption}
    \captionsetup{labelfont=normalfont,textfont=bf,justification=raggedright,singlelinecheck=off,labelsep=newline}
    \floatsetup[figure]{capposition=top}
    \floatsetup[table]{capposition=top}
    \pagenumbering{arabic}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo=FALSE,comment=FALSE,warning=FALSE,message=FALSE)
knitr::knit_hooks$set(plot = function (x, options) {
  float_correct <- function(f, y, opts)  {
    if (is.null(opts$regfloat) || opts$regfloat==FALSE)
      paste0(f(y, opts), "\n\n\\FloatBarrier\n")
    else
      f(y, opts)
  }
  if (!is.null(options$out.width) || !is.null(options$out.height) ||
      !is.null(options$out.extra) || options$fig.align != "default" ||
      !is.null(options$fig.subcap)) {
    if (is.null(options$fig.scap))
      options$fig.scap = NA
    return(float_correct(knitr:::hook_plot_tex, x, options))
  }
  return(float_correct(knitr:::hook_plot_md_base, x, options))
})

```

\newpage
\listoffigures

\listoftables
\newpage

# Introduction

`r content$text$intro_text`
  
\newpage

# Part 1: Reviewing the commonness of species reported in FAO Global

## Commonness of Taxonomic Group records in FishStatJ

```{r, com_isscaap_global,fig.cap="\\label{fig:com_isscaap_global}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_isscaap_global)

```

`r content$text$com_isscaap_global`

\newpage

## Commonness of Marine and anadromous vs Inland records in FishStatJ  

```{r, com_isscaap_area_type,fig.cap="\\label{fig:com_isscaap_area_type}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_isscaap_area_type)

```

`r content$text$com_isscaap_area_type`

\newpage

##  Commonness of Taxonomic Group records in FishStatJ — by Ocean Basin

```{r,com_isscaap_ocean ,fig.cap="\\label{fig:com_isscaap_ocean}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_isscaap_ocean)

```

`r content$text$com_isscaap_ocean`

\newpage

##  Commonness of Taxonomic Group records in FishStatJ — by FAO Fishery Areas

### Inland

```{r,com_isccap_f_area_inland ,fig.cap="\\label{fig:com_isccap_f_area_inland}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_isccap_f_area_inland)

```

`r content$text$com_isccap_f_area_inland`

\newpage

### Marine  

```{r,com_isccap_f_area_marine ,fig.cap="\\label{fig:com_isccap_f_area_marine}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_isccap_f_area_marine)

```

`r content$text$com_isccap_f_area_marine`

\newpage

# Part 2 Biodiversity reporting development in FAO Fisheries

##  Commonness among Pisces [vertebrate fish] records in FishStatJ — Global

```{r, com_sp_global,fig.cap="\\label{fig:com_sp_global}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_sp_global)

```

`r content$text$com_sp_global`

\newpage

##  Commonness among fish records in FishStatJ — by Ocean Basins

```{r,com_sp_ocean ,fig.cap="\\label{fig:com_sp_ocean}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_sp_ocean)

```

`r content$text$com_sp_ocean`

\newpage

##  Commonness among fish records in FishStatJ — By FAO Fisheries Areas

### Inland

```{r,com_sp_f_area_inland ,fig.cap="\\label{fig:com_sp_f_area_inland}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_sp_f_area_inland)

```

`r content$text$com_sp_f_area_inland`

\newpage

### Marine

```{r,com_sp_f_area_marine ,fig.cap="\\label{fig:com_sp_f_area_marine}Figure title", out.width = '100%'}

knitr::include_graphics(content$fig$com_sp_f_area_marine)

```

`r content$text$com_sp_f_area_marine`

\newpage
